---
output:
  pdf_document:
    keep_tex: true
    fig_caption: yes
    number_sections: yes
bibliography: Sections/bib/bibliography.bib
fontsize: 12pt
geometry: "left=1in,right=1in,top=1in,bottom=1in"
documentclass: article
spacing: double
header-includes:
  - \setlength{\parindent}{2em}
  - \setlength{\parskip}{0em}
  - \usepackage{placeins}
  - \usepackage{fancyhdr}
  - \usepackage{setspace}
  - \usepackage{chngcntr}
  - \usepackage{microtype}
  - \usepackage{ragged2e}
  - \usepackage{amsmath}
  - \usepackage{indentfirst}
  - \usepackage{longtable}
  - \usepackage{algorithm}
  - \usepackage{algpseudocode}
  - \onehalfspacing
  - \counterwithin{figure}{section}
  - \counterwithin{table}{section}
  - \linespread{2}
---


```{r global_options 1, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'h')
source("Sections/tables and figures/my_kable.R")
```


```{r title, child = 'Sections/00-Title.Rmd'}
```

\newpage
\normalsize
\singlespace
\tableofcontents
\doublespace
\newpage
\pagenumbering{arabic}

\fancypagestyle{plain}{%
  \renewcommand{\headrulewidth}{0pt}%
  \fancyhf{}%
  \fancyhead[R] \thepage
  \setlength\footskip{0pt}
}
\pagestyle{plain}
\justify

# Introduction

```{r child = 'Sections/01-Introduction.Rmd'}
```

# Literature Review

```{r child = 'Sections/02-Literature Review.Rmd'}
```

# Methodology

```{r child = 'Sections/03-Methodology.Rmd'}
```

# Results

```{r child = 'Sections/04-Results.Rmd'}
```


# Future Research and Conclusions

```{r child = 'Sections/05-Conclusions.Rmd'}
```

\newpage

# Appendix A: Full List of Spatial Lag Features

```{r child = 'Sections/06-Appendix A.Rmd'}
```

# References

---
metadata references not mentioned in paper:
nocite: | 
  @Johnson2007
  @Geltner2017
  @Almanie2015
  @Chapple2009
  @Chapple2016
  @Clay1979
  @Dietzell2014
  @Eckert1990
  @Fotheringham2015
  @Fu2014
  @Geltner2017
  @Guan2014
  @Helbich2013
  @Johnson2007
  @Kontrimasa2011
  @Koschinsky2012
  @Lees2008
  @Miller2015
  @Park2015
  @Pivo2011
  @Pollack2010
  @Quintos2013
  @Rafiei2016
  @Reardon2011
  @Schernthanner2016
  @Silverherz1936
  @Smith1979
  @Springer2017
  @Turner2001
  @urban2016
  @Watson2009
  @Zuk2015
  
...

