---
title: "Predicting Real Estate Sales Using Machine Learning and Spatial Dependence"
subtitle: "Boosting Random Forest Predictive Accuracy Using Spatial Lags"
output:
  pdf_document: 
    keep_tex: true
    toc: yes
    fig_caption: yes
header-includes:
  - \setlength{\parindent}{0em}
  - \setlength{\parskip}{1em}
bibliography: Sections/bib/bibliography.bib
---


# Introduction

```{r child = 'Sections/01-Introduction.Rmd'}
```

# Literature Review

```{r child = 'Sections/02-Literature Review.Rmd'}
```

# Methodology

```{r child = 'Sections/03-Methodology.Rmd'}
```

# Results

```{r child = 'Sections/04-Results.Rmd'}
```


# Conclusions and Future Research

```{r child = 'Sections/05-Conclusions.Rmd'}
```

# Appendix A: List of Spatial Lag Features

```{r child = 'Sections/06-Appendix A.Rmd'}
```

# References

---
metadata references not mentioned in paper:
nocite: | 
  @Johnson2007
  @Geltner2017
  @Almanie2015
  @Chapple2009
  @Chapple2016
  @Clay1979
  @Dietzell2014
  @Eckert1990
  @Fotheringham2015
  @Fu2014
  @Geltner2017
  @Guan2014
  @Helbich2013
  @Johnson2007
  @Kontrimasa2011
  @Koschinsky2012
  @Lees2008
  @Miller2015
  @Park2015
  @Pivo2011
  @Pollack2010
  @Quintos2013
  @Rafiei2016
  @Reardon2011
  @Schernthanner2016
  @Silverherz1936
  @Smith1979
  @Springer2017
  @Turner2001
  @urban2016
  @Watson2009
  @Zuk2015
  
...