---
title: "Motivating Example"
output: github_document
---


```{r setup, include = FALSE}
require("knitr")
opts_knit$set(root.dir = "/Users/timkiely/Dropbox (Personal)/MSPA/Thesis/Analysis/nyc-sales-data")
```

```{r}
source("R/helper/load-packages.R")
source("R/helper/source-files.R")
```


```{r}
base1 <- read_rds("data/aux data/sample_p06_base_model_data.rds")
radii_index <- read_rds("data/aux data/radii-index.rds")
radii_data <- radii_index %>% st_set_geometry(NULL)
radii_data$lon <- st_coordinates(radii_index)[,1]
radii_data$lat <- st_coordinates(radii_index)[,2]

inverted_normalized_distance <- function(x){
  x <- if_else(x!=0,1/x,0)
  x <- x/sum(x, na.rm = TRUE)
  x <- if_else(is.nan(x),0,x)
}

distance_weighted_mean <- function(x, w) weighted.mean(x, w, na.rm = T)
sf_weighted_mean <- function(x, w) weighted.mean(x, w, na.rm = T)
distance_weighted_mean_sf_concious <- function(x, w) weighted.mean(x, w, na.rm = T)
combined_weighted_mean <- function(x, w) weighted.mean(x, w, na.rm = T)
radii_mean <- function(x) mean(x, na.rm = T)
range01 <- function(x){(x-min(x))/(max(x)-min(x))}
```

Visualizing the SMA and EMA features on in W27th data:

```{r message=FALSE, warning=FALSE}
w27st <- base1 %>% filter(bbl == '1_829_16') 
w27st %>% 
  filter(!is.na(Last_Sale_Price)) %>% 
  ggplot()+
  aes(x = Year, y = Last_Sale_Price, group = 1)+
  geom_col()+
  geom_col(aes(y = `SALE PRICE`), fill = "blue")+
  geom_line(aes(y = SMA_Price_2_year))+
  geom_line(aes(y = SMA_Price_3_year))+
  geom_line(aes(y = SMA_Price_5_year))+
  geom_line(aes(y = EMA_Price_2_year), col = "red")+
  geom_line(aes(y = EMA_Price_5_year), col = "darkred")

```

Here is a picture of the euclidean distance:

```{r}

w27st_sf <- w27st %>% distinct(address, lon, lat) %>% st_as_sf(coords = c("lon","lat"), crs = 4326) %>% st_transform(32618)

euc_dists <- 
  radii_data %>% 
  filter(bbl == '1_829_16') %>% 
  select(bbl, lat, lon, Building_Type, BldgArea, neighbors) %>% 
  unnest() %>% 
  left_join(select(radii_data, bbl, "lat_neighbor" = lat
           , "lon_neighbor" = lon,"Nieghbor_BT" = Building_Type
           , "Neighbor_SF" = BldgArea)
    , by = c('neighbors'='bbl')
    ) %>% 
  mutate(Euc_distance = sqrt((lat_neighbor-lat)^2+(lon_neighbor - lon)^2)) %>% 
  st_as_sf(coords = c("lon_neighbor", "lat_neighbor"), crs = 32618)

euc_dists %>% 
  ggplot(aes(col = Euc_distance))+
  geom_sf()+
  geom_sf(data = w27st_sf, col = "red")+
  labs(title = "Basic euclidean distance")

```

After inveting the euclidean distance, and dropping unlike building types to 0 weight, the inverted distance weight looks like the following:

```{r}
euc_data <- 
  radii_data %>% 
  filter(bbl == '1_829_16') %>% 
  select(bbl, lat, lon, Building_Type, BldgArea, neighbors) %>% 
  unnest() %>% 
  left_join(select(radii_data, bbl
                   , "lat_neighbor" = lat
                   , "lon_neighbor" = lon
                   , "Nieghbor_BT" = Building_Type
                   , "Neighbor_SF" = BldgArea)
            , by = c('neighbors'='bbl')
            ) %>% 
  mutate(Euc_distance = sqrt((lat_neighbor-lat)^2+(lon_neighbor - lon)^2)) %>%
  # distance metrics. Currently using absolute euclidean distance, and Square Footage
  
  # if neighbor building type is not same as origin, set distance to max (weight becomes 0)
  mutate(Euc_distance = ifelse(Building_Type == Nieghbor_BT, Euc_distance, max(Euc_distance))) %>% 
  
  # inverting and normalizing. Closer observations are more alike
  group_by(bbl) %>% 
  mutate(euc_weight = max(Euc_distance)-Euc_distance) %>% 
  ungroup() %>% 
  select(lat_neighbor, lon_neighbor, euc_weight) %>% 
  st_as_sf(coords = c("lon_neighbor","lat_neighbor"))
  
euc_data %>% 
  ggplot()+
  aes(col = euc_weight)+
  geom_sf()

```


```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(leaflet)
euc_data %>% st_set_crs(32618) %>% st_transform(4326) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers() %>% 
  addCircleMarkers(data = w27st_sf%>% st_transform(4326), col = "red")
```


Visualize the pattern of sales by year around W27th:

```{r}

radii_data %>% 
  filter(bbl == '1_829_16') %>% 
  filter(!is.na(Year)) %>% 
  select(bbl, lat, lon, Building_Type, BldgArea, neighbors) %>% unnest() %>% 
  left_join(select(radii_data, bbl, "lat_neighbor" = lat
           , "lon_neighbor" = lon,"Nieghbor_BT" = Building_Type
           , "Neighbor_SF" = BldgArea)
    , by = c('neighbors'='bbl')) %>% ungroup() %>% select(bbl, neighbors, lat_neighbor, lon_neighbor) %>% 
  left_join(select(base1, Year, bbl, Sold), by = c('neighbors'='bbl')) %>% 
  st_as_sf(coords = c("lon_neighbor", "lat_neighbor"), crs = 32618) %>% 
  arrange(Sold) %>% 
  ggplot()+
  geom_sf(size = 0.00001)+
  aes(col = Sold)+
  facet_wrap(~Year)+
  theme(legend.position = "none")+
  labs(x = NULL, y = NULL)

```


```{r}
radii_data %>% 
  filter(bbl == '1_829_16') %>% 
  filter(!is.na(Year)) %>% 
  select(bbl, lat, lon, Building_Type, BldgArea, neighbors) %>% unnest() %>% 
  left_join(select(radii_data, bbl, "lat_neighbor" = lat
           , "lon_neighbor" = lon,"Nieghbor_BT" = Building_Type
           , "Neighbor_SF" = BldgArea)
    , by = c('neighbors'='bbl')) %>% ungroup() %>% select(bbl, neighbors, lat_neighbor, lon_neighbor) %>% 
  left_join(select(base1, Year, bbl, Sold), by = c('neighbors'='bbl')) %>% 
  select(bbl, neighbors, Year, Sold) %>% 
  group_by(neighbors) %>% 
  summarise(sum(Sold))
```


We can see that sales seem to co-occur in the area:

```{r message=FALSE, warning=FALSE}

radius_sales <- radii_data %>% 
  filter(bbl == '1_829_16') %>% 
  filter(!is.na(Year)) %>% 
  select(bbl, lat, lon, Building_Type, BldgArea, neighbors) %>% unnest() %>% 
  left_join(select(radii_data, bbl, "lat_neighbor" = lat
                   , "lon_neighbor" = lon,"Nieghbor_BT" = Building_Type
                   , "Neighbor_SF" = BldgArea)
            , by = c('neighbors'='bbl')) %>% ungroup() %>% select(bbl, neighbors, lat_neighbor, lon_neighbor) %>% 
  left_join(select(base1, Year, SALE_DATE, bbl, Sold), by = c('neighbors'='bbl')) %>% 
  mutate(Sale_Month = lubridate::month(SALE_DATE)) %>% 
  filter(!is.na(Sale_Month)) %>% 
  group_by(Year, Sale_Month) %>% 
  summarise(Sold_In_Year = sum(Sold)
            , Total_in_Year = n()
            , Percent_Sold_in_Year = Sold_In_Year/Total_in_Year) %>% 
  mutate(Sale_YearMonth = as.Date(paste0(Year,"-",Sale_Month,"-1"))) %>% 
  select(Sale_YearMonth, Sold_In_Year)

w27_sales <- w27st %>% 
  mutate(Sale_Month = lubridate::month(SALE_DATE)) %>% 
  select(Sale_Month, SALE_DATE, Year, "Building_Sold" = Sold) %>% 
  filter(!is.na(Sale_Month)) %>% 
  mutate(Sale_YearMonth = as.Date(paste0(Year,"-",Sale_Month,"-1"))) %>% 
  select(Sale_YearMonth, Building_Sold)

all_dates <- data_frame(date = seq.Date(from = as.Date("2003-01-01"), to = as.Date("2017-12-01"), by = "month"))

all_dates %>% 
  left_join(radius_sales, by = c("date" = "Sale_YearMonth")) %>% 
  left_join(w27_sales, by = c("date" = "Sale_YearMonth") ) %>% 
  ggplot()+
  aes(x = date, y = Sold_In_Year)+
  geom_col()+
  geom_col(aes(y = Building_Sold), fill = "red")+
  geom_smooth(se = F)


```


```{r}

radius_sales_sf <- radii_data %>% 
  filter(bbl == '1_829_16') %>% 
  filter(!is.na(Year)) %>% 
  select(bbl, lat, lon, Building_Type, BldgArea, neighbors) %>% unnest() %>% 
  left_join(select(radii_data, bbl, "lat_neighbor" = lat
                   , "lon_neighbor" = lon,"Nieghbor_BT" = Building_Type
                   , "Neighbor_SF" = BldgArea)
            , by = c('neighbors'='bbl')) %>% ungroup() %>% select(bbl, neighbors, lat_neighbor, lon_neighbor, Neighbor_SF) %>% 
  left_join(select(base1, Year, SALE_DATE, bbl, Sold), by = c('neighbors'='bbl')) %>% 
  mutate(Sale_Month = lubridate::month(SALE_DATE)) %>% 
  filter(!is.na(Sale_Month)) %>% 
  group_by(Year, Sale_Month) %>% 
  summarise(Sold_In_Year = sum(Sold)
            , Total_in_Year = n()
            , Percent_Sold_in_Year = Sold_In_Year/Total_in_Year) %>% 
  mutate(Sale_YearMonth = as.Date(paste0(Year,"-",Sale_Month,"-1"))) %>% 
  select(Sale_YearMonth, Sold_In_Year)

w27_sales <- w27st %>% 
  mutate(Sale_Month = lubridate::month(SALE_DATE)) %>% 
  select(Sale_Month, SALE_DATE, Year, "Building_Sold" = Sold) %>% 
  filter(!is.na(Sale_Month)) %>% 
  mutate(Sale_YearMonth = as.Date(paste0(Year,"-",Sale_Month,"-1"))) %>% 
  select(Sale_YearMonth, Building_Sold)

all_dates <- data_frame(date = seq.Date(from = as.Date("2003-01-01"), to = as.Date("2017-12-01"), by = "month"))

all_dates %>% 
  left_join(radius_sales, by = c("date" = "Sale_YearMonth")) %>% 
  left_join(w27_sales, by = c("date" = "Sale_YearMonth") ) %>% 
  ggplot()+
  aes(x = date, y = Sold_In_Year)+
  geom_col()+
  geom_col(aes(y = Building_Sold), fill = "red")+
  geom_smooth(se = F)

```

Look at the predictions and see how they match up against actual:

```{r}
radii_data_infile <- read_rds('results/prob/p11_prob_of_sale_model_radii.rds')
radii_model <- radii_data_infile$model

radii_model_data <- read_rds("/Users/timkiely/Dropbox (Personal)/MSPA/Thesis/Analysis/nyc-sales-data/data/processing steps/p08_radii_model_data.rds")

h2o.init()
the_preds <- predict(radii_model, newdata = as.h2o(radii_model_data))

radii_model_data_sales <- radii_model_data %>% 
  bind_cols(as_data_frame(the_preds$predict)) %>%
  bind_cols(as_data_frame(the_preds$p1))

w27_sales <- radii_model_data_sales %>% 
  filter(bbl == '1_829_16') %>% 
  select(Year, Sold, predict, p1)

w27_sales %>% 
  mutate(predict = as.integer(predict)) %>% 
  mutate(predict = ifelse(predict==1,0,1)) %>% 
  ggplot()+
  aes(x = Year)+
  geom_col(aes(y = Sold))+
  geom_point(aes(y = predict), color = "red")+
  geom_line(aes(y = p1), color = "green")+
  theme_bw()+
  labs(title = "Probability of Sale, Prediction and Outcome for Single Office Property in NYC"
       , subtitle = "Red dots are predictions, black bars are actual sales, green line is probability of sale"
       , y = "Probability of Sale"
       , x = NULL)

```









